### 2023-02-15 notebooks/conformal.qmd
slowly slowly

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult)
```

>>>>

```{julia}
contourf(mach.model, mach.fitresult, X, y; plot_set_size=true)
```

## Counterfactual Explanation

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult)
generator = CCE.ConformalGenerator()
```

```{julia}
x = select_factual(counterfactual_data,rand(1:size(counterfactual_data.X,2)))
y = predict_label(M, counterfactual_data, x)[1]
target = counterfactual_data.y_levels[counterfactual_data.y_levels .!= y][1]
```
